Replication in Archaeological Science: Shape as a Measure of Weapon Standardisation

### 2020-02-24 analysis/paper.Rmd
explored parameters of the ANOVA test

>>>>

We can explore the effect of other parameters in the allometry ANOVA, to test whether the core conclusion holds. In the example below, we do not log-transform the size variable and we set a signficance threshold (alpha) of 0.1, rather than the default 0.05.

```{r explore ANOVA  test v1, include=TRUE, echo=FALSE}
lances_ANOVA_two<-procD.allometry(shape ~ size, ~site, logsz=FALSE, seed=42, alpha=0.1, data=lances_geomorph, method="PredLine")

print(lances_ANOVA_two)

The core result holds! We can push these boundaries futher; removing residual randomnizatio and using Cohen’s f-squared values as the random distribution to
estimate effect size.

```{r explore ANOVA  test v2, include=TRUE, echo=FALSE}
lances_ANOVA_three <- procD.allometry(shape ~ size, ~site, logsz=FALSE, seed=42, alpha=0.1, effect.type="cohen", RRPP=FALSE, data=lances_geomorph, method="PredLine")

print(lances_ANOVA_three)

The core result still holds.
